---
output: github_document
editor_options: 
  chunk_output_type: console
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "##",
  fig.path = "README-",
  message = FALSE, 
  warning = FALSE,
  fig.retina = 2
)
options(width = 120)
```


# ssllabs

Interrogate SSL Certificate Configuration Efficacy via 'ssllabs' API

## Description

'Qualys' provides a free online service (<https://www.ssllabs.com/ssltest/index.html>)
that performs a deep analysis of the configuration of any SSL web server on 
the public Internet. Methods are provides to initiate scans and retreive 
scan results.

## What's Inside the Tin?

The following functions are implemented:

- `analyze_site`:	Invoke assessment and check progress
- `get_endpoint_data`:	Retrieve detailed endpoint information
- `get_root_certs_raw`:	Retrieve root certificates
- `ssllabs_api_info`:	Check SSL Labs availability

## Installation

```{r eval=FALSE}
install.packages("ssllabs", repos = "https://cinc.rud.is/")
```

## Usage

```{r}
library(ssllabs)

# current verison
packageVersion("ssllabs")

ssllabs_api_info() %>% 
  str(1)

get_root_certs() %>% 
  str(1)

get_endpoint_data(
  host = "www.ssllabs.com",
  ip = "64.41.200.100", 
  from_cache = TRUE
)

analyze_site(
  host = "www.ssllabs.com", 
  from_cache = TRUE
) %>% 
  str(2)
```

## `ssllabs` Metrics

```{r cloc, echo=FALSE}
cloc::cloc_pkg_md()
```

## Code of Conduct

Please note that this project is released with a [Contributor Code of Conduct](CONDUCT.md). 
By participating in this project you agree to abide by its terms.
