---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

<!-- 
[![Build Status](https://travis-ci.org/hrbrmstr/ssllabs.svg)](https://travis-ci.org/hrbrmstr/ssllabs) 
![Project Status: Concept - Minimal or no implementation has been done yet.](http://www.repostatus.org/badges/0.1.0/concept.svg)](http://www.repostatus.org/#concept)
[![CRAN_Status_Badge](http://www.r-pkg.org/badges/version/ssllabs)](http://cran.r-project.org/web/packages/ssllabs) 
![downloads](http://cranlogs.r-pkg.org/badges/grand-total/ssllabs)
-->

`ssllabs` : Tools to Work with the `SSL Labs` `API`

The following functions are implemented:

- `analyze_site`:	Invoke assessment and check progress
- `get_endpoint_data`:	Retrieve detailed endpoint information
- `get_root_certs_raw`:	Retrieve root certificates
- `get_status_codes`:	Retrieve known status codes
- `ssllabs`:	Tools to Work with the 'SSL Labs' 'API'
- `ssllabs_api_info`:	Check SSL Labs availability

### Installation

```{r eval=FALSE}
devtools::install_github("hrbrmstr/ssllabs")
```

```{r echo=FALSE, message=FALSE, warning=FALSE, error=FALSE}
options(width=120)
```

### Usage

```{r}
library(ssllabs)

# current verison
packageVersion("ssllabs")

ssllabs_api_info()

get_status_codes()

get_root_certs_raw()

analyze_site("rud.is")
```

### Test Results

```{r}
library(ssllabs)
library(testthat)

date()

test_dir("tests/")
```

### Code of Conduct

Please note that this project is released with a [Contributor Code of Conduct](CONDUCT.md). 
By participating in this project you agree to abide by its terms.
